Thermodynamic fragments in magic state theories

### 2020-10-21 magic_paper.tex
Added discussion on Lorenz curve comparison for state conversion

\subsubsection{Lorenz curve comparison}
According to~\cref{thm:dmajor}, a necessary condition for $\rho \xrightarrow{\E \in \O_\sigma} \tau$ is that $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$.
We can reduce this condition to a finite set of inequalities, defined at the elbows of $\lc{\tau}{\sigma}(x)$.
\begin{theorem}\label{thm:elbows}
	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$-fragment.
	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff the elbows of $\lc{\tau}{\sigma}(x)$ lie vertically below $\lc{\rho}{\sigma}(x)$.
\end{theorem}
\begin{proof}
	Let $n$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $T \coloneqq \{x_0, x_1, \dots, x_n, x_{n+1} \}$ be the set of the elbows' $x$-coordinates including $x_0 = 0$ and $x_{n+1} = 1$.

@@

Consider now the magic state conversion,
\begin{equation}\label{eq:su_conversion}
	\noisysn \xrightarrow{\E \in \O_{\id/d}} \rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}.
\end{equation}
The Lorenz curve comparison of these states gives rise to $k$ independent necessary constraints
\begin{align}
\lc{\noisysn}{\frac{1}{d}\id}(x_1) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_1), \nonumber\\
\lc{\noisysn}{\frac{1}{d}\id}(x_2) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_2), \nonumber\\
&\vdotswithin{=} \nonumber\\
\lc{\noisysn}{\frac{1}{d}\id}(x_k) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_k), \nonumber
\end{align}
where $x_1, x_2, \dots, x_k$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}$.

>>>>

\subsubsection{Lorenz curve comparison}
Consider the magic state conversion,
\begin{equation}\label{eq:su_conversion}
	\noisysn \xrightarrow{\E \in \O_{\id/d}} \rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}.
\end{equation}
Pointwise comparison of the initial and final state Lorenz curves is non-trivial, since the elbows of the curves do not align veritically.
The initial state Lorenz curve consists of
\begin{equation}
	\sum_{j=0}^{n} c_j = 9^n
\end{equation}
\nick{technically $(9^n+1)$ because 0 is artificially added in the end} points with $x$-coordinates incrementing by $\frac{1}{9^n}$ which we denote as the set 
\begin{equation}
X \coloneqq \left\{ \sum_{i=0}^{k} \frac{i}{9^n} \right\}_{0 < k \leq 9^n}.
\end{equation}

The final state Lorenz curve consists of $9^k (< 9^n)$ points and, in order to make a pointwise comparison, we rewrite it as
\begin{equation}
\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k} \otimes \left( \frac{1}{d}\id\right)^{\otimes(n-k)},
\end{equation}
with transformed Wigner components $w_j^\prime = d^{-2(n-k)}w_j$ and multiplicities $c_j^\prime = d^{2(n-k)}c_j$, where $w_j, c_j$ are given in~\cref{tab:lcsu_w} for $j=0,\dots,k$.
The Lorenz curve of the final state remains the same, but now it consists of $9^n$ points with the same $x$-coordinates as the initial state.
Therefore, we can compare the curves pointwise with $9^n$ inequalities of the form
\begin{equation}\label{eq:lc_pointwise}
\lc{\noisysn}{\frac{1}{d}\id}(x) \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x)
\end{equation}
for all $x \in X$.

According to~\cref{thm:dmajor}, a necessary condition for $\rho \xrightarrow{\E \in \O_\sigma} \tau$ is that $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$.
We can reduce the inequalities in~\cref{eq:lc_pointwise} significantly with the following result.
\begin{theorem}\label{thm:elbows}
	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$-fragment.
	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff the elbows of $\lc{\tau}{\sigma}(x)$ lie vertically below $\lc{\rho}{\sigma}(x)$.
\end{theorem}
\begin{proof}
	Let $n$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $T \coloneqq \{x_0, x_1, \dots, x_n, x_{n+1} \}$ be the set of the elbows' $x$-coordinates including $x_0 = 0$ and $x_{n+1} = 1$.

@@

Returning to~\ref{eq:su_conversion}, the $k$ independent necessary constraints are
\begin{align}
\lc{\noisysn}{\frac{1}{d}\id}(x_1) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_1), \nonumber\\
\lc{\noisysn}{\frac{1}{d}\id}(x_2) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_2), \nonumber\\
&\vdotswithin{=} \nonumber\\
\lc{\noisysn}{\frac{1}{d}\id}(x_k) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_k), \nonumber
\end{align}
where $x_1, x_2, \dots, x_k \in X$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}$.
